Papers

### 2025-12-23 quarto/index.qmd
update

**Aston Zhang** is a member of technical staff at <a href="https://openai.com" target="_blank">OpenAI</a>. 
His work has been recognized with the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
the ACM Ubicomp Distinguished Paper Award,
and an ACM SenSys Best Paper Award nomination.
His textbook, "<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>," 
is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He earned his Ph.D. from UIUC.

@@

@@

>>>>

**Aston Zhang** is a member of technical staff at <a href="https://openai.com" target="_blank">OpenAI</a>. 
His work has been recognized with the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
the ACM Ubicomp Distinguished Paper Award,
and an ACM SenSys Best Paper Award nomination.
His textbook, "<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>," 
is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He earned his Ph.D. from the University of Illinois Urbana-Champaign.

@@

* R. Bansal, **A. Zhang**, R. Tiwari, L. Madaan, S. Duvvuri, D. Khatri, D. Brandfonbrener, D. Alvarez-Melis, P. Bhargava, M. Kale, and S. Jelassi<br>
<a href="https://arxiv.org/abs/2512.13898" target="_blank">Let's (NoT) Just Put Things in Context: Test-Time Training for Long-Context LLMs</a><br>
*Lightweight context-specific training is a better use of inference compute for long context.* In *arXiv*, 2026<br>

@@

* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
	<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
	In *Empirical Methods in Natural Language Processing* (**EMNLP**), 2023<br>
